Supervised Learning for Psychological Attention to High School Students

### 2020-11-17 article/article.tex
[ article ] Corrected typo.

As a result, schools and parents have an important responsibility to the
students of creating this environment and wisely handling mental health issues.
However, high schools do not always know how to handle or detect cases of mental
health issues. Additionally, technology has led to targeted harassing becoming
more popular over time, therefore, difficulting the probability of detecting
these cases.

@@

The results are presented using three learning curves: the sum of local
gradients per layer at the end of each epoch, the average error energy and a
Receiver Operating Characteristic (ROC) curve, comparing the obtained results
with the real labels.
\begin{itemize}
  \item The sum of gradients per layer at the end of each epoch is an approach
  visualizing if the training algorithm is solving the optimization problem,
  since the sum of local gradients must converge to zero as each gradient
  converges to zero. It is well-known that the vanish of gradients is a
  necessary condition for optimality and the training algorithm is just an
  optimization problem minimizing the output error (cost function).
  \item The average error energy is the cost function of the optimization
  problem. Let $y_i\in\mathbb{R}^n$ be the real output of a given input pattern
  $x_i\in\mathbb{R}^m$ and let $\hat{y}_i\in\mathbb{R}^n$ be the output of the
  NN for the same input pattern. Denoting each component by superscripts, the
  average error energy $\xi_{av}$ on each epoch is then computed as
  \begin{equation}
    \xi_{av}=\dfrac{1}{2}\sum_{i=1}^{N}\sum_{k=1}^n\left(y^k_i-\hat{y}^k_i\right)^2,
  \end{equation}
  where $N$ is the training sample size. Thus, it is clear that
  $\xi_{av}\rightarrow0$ as the training algorithm solves the learning problem
  well.
  \item The ROC curve is a tool that helps visualize the correct clasifications
  of the learning machine by plotting the true positive rate on the vertical
  axis, and false positive rate on the horizontal axis. The Area Under the Curve
  (AUC) is an indicator of how good the data is being classified by the model,
  with higher values being better usually better.
\end{itemize}

>>>>

As a result, schools and parents have an important responsibility to the
students of creating this environment and wisely handling mental health issues.
However, high schools do not always know how to handle or detect cases of mental
health issues. Additionally, technology has led to targeted harassing becoming
more popular over time, therefore, complicating the probability of detecting
these cases.

@@

The results are presented using three learning curves: the sum of local
gradients per layer at the end of each epoch, the average error energy and a
Receiver Operating Characteristic (ROC) curve, comparing the obtained results
with the real labels.
\begin{itemize}
  \item The sum of gradients per layer at the end of each epoch is an approach
  visualizing if the training algorithm is solving the optimization problem,
  since the sum of local gradients must converge to zero as each gradient
  converges to zero. It is well-known that the vanish of gradients is a
  necessary condition for optimality and the training algorithm is just an
  optimization problem minimizing the output error (cost function).
  \item The average error energy is the cost function of the optimization
  problem. Let $y_i\in\mathbb{R}^n$ be the real output of a given input pattern
  $x_i\in\mathbb{R}^m$ and let $\hat{y}_i\in\mathbb{R}^n$ be the output of the
  NN for the same input pattern. Denoting each component by superscripts, the
  average error energy $\xi_{av}$ on each epoch is then computed as
  \begin{equation}
    \xi_{av}=\dfrac{1}{2}\sum_{i=1}^{N}\sum_{k=1}^n\left(y^k_i-\hat{y}^k_i\right)^2,
  \end{equation}
  where $N$ is the training sample size. Thus, it is clear that
  $\xi_{av}\rightarrow0$ as the training algorithm solves the learning problem
  well.
  \item The ROC curve is a tool that helps visualize the correct classifications
  of the learning machine by plotting the true positive rate on the vertical
  axis, and false positive rate on the horizontal axis. The Area Under the Curve
  (AUC) is an indicator of how good the data is being classified by the model,
  with higher values being better usually better.
\end{itemize}
